Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.

### 2015-05-01 papers/MbhMsph/mm.tex
friday climb

\title{Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.}

@@

\begin{abstract}
We present correlations between black hole mass, $M_{\rm BH}$, 
and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
and the spheroid's stellar mass, $M_{\rm *,sph}$,
built upon a high-quality data set.
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
%which is minimally affected by dust and star formation. 
%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
and were derived from our state-of-the-art multicomponent galaxy decompositions 
that, for the first time, were checked to be consistent with the galaxy kinematics. 
{\bf limit of 250 words, no room for mentioning the gaalxy components, more appropriate for data paper}
Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
%We provide updated linear regressions 
%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
We conclude that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
We decided to vary only the errors associated to $L_{\rm gal}$ 
because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 

@@

In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{explain}.

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 

@@

\subsection{Pseudo- versus classical bulges}
korm. review \\
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$, 
plotted against $n_{\rm sph}$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:pseudob}
\end{center}
\end{figure}

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans.
For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }

\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
{\bf cite Anne's paper}\\
{\bf AL: however we analyze the agns in another paper, blah blah}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type.
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. {\bf key result}}
\label{fig:mbhmasssph}
\end{center}
\end{figure}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle M_{\rm *,sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - \langle M_{\rm *,sph} \rangle)/{\rm M_\odot}]$} \\ [0.5em]
{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10.81$ & $-$ & $0.48$ \\
                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10.81$ & $-$ & $0.59$ \\
                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10.81$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10.81$ & $-$                    & $0.51$ \\
                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.19$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]

>>>>

\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}

@@

\begin{abstract}
We present correlations between black hole mass, $M_{\rm BH}$, 
and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
and the spheroid's stellar mass, $M_{\rm *,sph}$,
built upon a high-quality data set.
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
%which is minimally affected by dust and star formation. 
%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
and were derived from our state-of-the-art multicomponent galaxy decompositions 
that, for the first time, were checked to be consistent with the galaxy kinematics. 
{\bf limit of 250 words, no room for mentioning the gaalxy components, more appropriate for data paper}
Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
%We provide updated linear regressions 
%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ log-correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ log-correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
We decided to vary only the errors associated to $L_{\rm gal}$ 
because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{The classification has changed for the galaxies 
NGC 1316, NGC 1332 and NGC 3998.} from the classification used here, 

@@

In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 
disks of stars fully embedded in the spheroidal component of their galaxy. 
They are typical of ``disky'' elliptical galaxies (e.g.~NGC 3377), 
but they can also be found in other types of host galaxies.
They can be considered an intermediate class between nuclear disks, with sizes $\sim$$10-100\rm~pc$, %%
and large-scale disks, that encase the bulge and dominate the light at large radii.}. 

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ log-correlation -- 

@@

\subsection{Pseudo- versus classical bulges}
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
Among the 23 bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset. 
\cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
and cautions that each individual criterion has a failure rate of 0-25\% \citep{fisherdrory2015}. 
If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges have negative vertical offset. 
What we observe, instead, is that there are the same number of $n_{\rm sph}<2$ bulges lying above and below 
the correlation defined by $n_{\rm sph}>2$ bulges\footnote{One 
reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$. 
In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation of $n_{\rm sph}>3$ bulges.}, 
and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$, 
plotted against $n_{\rm sph}$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Among bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset.
Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:pseudob}
\end{center}
\end{figure}

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans. 
More data would be welcome to better constrain the slope of this \emph{blue sequence}.
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $2.28^{+1.67}_{-1.01}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies.

\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated careful analysis. \\

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type.
The red dashed line indicates the BCES bisector linear regression for the bulges of early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
a near-linear relation consistent with a dry-merging formation scenario.
The blue solid line shows the BCES bisector linear regression for the bulges of late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge. }
\label{fig:mbhmasssph}
\end{center}
\end{figure}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle M_{\rm *,sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - \langle M_{\rm *,sph} \rangle)/{\rm M_\odot}]$} \\ [0.5em]
 Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $11.28$ & $-$ & $0.42$ \\
 			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $11.28$ & $-$ & $0.61$ \\
 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $11.28$ & $-$ & $0.47$ \\
 			& FITEXY $(Y|X)$    & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $11.28$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
 			& FITEXY $(X|Y)$    & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $11.28$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
 			& FITEXY Bisector   & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $11.28$ & $-$                    & $0.46$ \\
 			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $11.28$ & $0.40 \pm 0.09$ & $0.42$ \\
 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $11.28$ & $0.67 \pm 0.30$ & $0.65$ \\
 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $11.28$ & $-$	& $0.45$ \\
